PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-27 paper.tex
Update on Overleaf.
CERE checked protocol

  \begin{itemize}
  \item
    \textbf{explain the purpose of the study: showing robots how
    children play}
    \item
    in condition B, present briefly the robot -- saying it is not a very
    sociable robot, and it might play alone.
  \item
    place children on cushions
  \item
    give them the yellow/purple sport bibs
  \item
    make sure their hair is tied back (to help with face tracking)
  \item
    ask names (but do not write them down)
  \item
     complete questionnaire on the tablet -- age, gender, familiarity with
    tablet
  \item
    \textbf{remind the children that they can withdraw at anytime}

  \end{itemize}
\item
  visual focus task (30 seconds)
\item
  tutorial (1-2 min): explain how to interact with the game, ensure the
  children are confident with the manipulation/drawing
\item
  main freeplay task (up to 40 min):

  \begin{itemize}
  \item
    start the recording
  \item
    example prompt: ``I let you play now! You can build a zoo, or tell
    stories, as you want''
  \item
    let children play
  \item
    encourage children to keep playing at least 5 min
  \item
    once they wish to stop, stop recording
  \end{itemize}
\item
  debriefing (5 min):

  \begin{itemize}
  \item
    answer possible questions from the children
  \item
    give stickers
  \end{itemize}
\end{enumerate}

@@

Total duration: 30 minutes per group.

>>>>

  \begin{itemize}
  \item
    \textbf{explain the purpose of the study: showing robots how
    children play}
    \item
    briefly present the robot -- it gives a short message dependent on condition (Condition A: "Hello, I'm Nao. Today, I'll be watching you while you play and soon I'll be able to play with you. Is that alright?"; Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")
  \item
    place children on cushions
  \item
    give them the yellow/purple sport bibs
  \item
    make sure their hair is tied back (to help with face tracking)
  \item
    ask names (but do not write them down)
  \item
     complete questionnaire on the tablet -- age, gender, familiarity with
    tablet
  \item
    \textbf{remind the children that they can withdraw at anytime}

  \end{itemize}
\item
  Visual focus task (30 seconds)
\item
  Tutorial (1-2 min): explain how to interact with the game, ensure the
  children are confident with the manipulation/drawing
%CERE Are we mentioning the object placement task?
\item
  Freeplay task (up to 40 min):

  \begin{itemize}
  \item
    start the recording
  \item 
     Condition B only: Set up and localise robot (1-3 min)
  \item
    example prompt: ``Just to remind you, you can use the animals or draw. Whatever you like. 
    If you run out of ideas, there's also an ideas box. For example, the first one is a zoo. You could draw a zoo or tell a story. 
    When you get bored or 
    don't want to play anymore, just let me know."
  \item
    let children play
  \item
    encourage children to keep playing at least 5 min
  \item
    once they wish to stop, stop recording
  \end{itemize}
\item
  Debriefing (5 min):

  \begin{itemize}
  \item
    answer possible questions from the children
  \item
    give stickers as a thank you
  \end{itemize}
\end{enumerate}

@@

Total duration: between 20-50 min.
